\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/eval.tex
formatting in 6.
eval

To begin, we first implement the benchmarks from Bost et al.~\cite{shafindss}
and \minion~\cite{minionn} (both of which study the same setting),
and show that the performance of the high-level code written in \tool
is comparable to their hand-crafted circuits
(Section~\ref{sec:shallow} and Section~\ref{sec:dnneval}).
%
Next, we demonstrate the generality and programmability aspects of
\tool by implementing state-of-the-art machine learning models from
Tensorflow~\cite{tensorflow} and \bonsai~\cite{bonsai}. Indeed, we
provide the first 2PC implementation of \bonsai.
%
Finally, we
implement a Deep Neural Network (DNN) for CIFAR-10
dataset~\cite{cifar} from \minion~\cite{minionn} to illustrate the use
of partitioning in \tool.

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms resp. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM.
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Since most of our benchmarks
are related to machine learning, we set up some notation (largely
standard in machine learning) and describe our benchmarks next.

@@

We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. Further, given a vector $x\in\R^d$, we say $\mathsf{argmax}\ x = i$ if $x_i = \mathsf{max}\ \{x_1,\ldots,x_d\}$. We focus on the machine learning models for {\it classification}. A classifier $C$ uses a trained model to {\it predict} a
label $\ell$ for an input data point $x$. For example, given a
data point which is a tuple of height and weight of an individual,
a classifier might be able to predict a label as ``male'' or ``female''. The {\it
  accuracy} of a classifier refers to the fraction of data points that
the classifier labels correctly from a given set of test data
points.

\subsubsection*{Standard classifiers}
A {\em binary linear classifier} is one of the simplest classifiers. Here,
the input is a data point $x\in\R^d$,
and the model is a vector $w\in\R^d$. The possible labels are
$\ell\in\{\mathit{true},\mathit{false}\}$ and the classifier is
$C_w\equiv w^T\matmul x>0$, where $w^T$ denotes the transpose
of matrix $w$, $\matmul$ denotes matrix multiplication (with a vector in this case) and $a>b$ returns $1$ if $a>b$ and $0$ otherwise. This classifier requires $d$ multiplications, $d-1$
additions, and a single comparison.

A more interesting classifier is {\em Na\"{i}ve Bayes} that predicts labels
from the set $[n]$.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
The model has two matrices: a vector $P$ of length $n$ s.t. for each
$i
\in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood
%that the output label is $i$ for $i\in[n]$.
The other matrix $T$ has size $d\times F\times n$ and for each $j\in
[d], k\in [F], i\in [n]$, the entry $T(j)(k)(i)$ is 
%\equiv\log p(x_j|\ell=i)$, i.e.,
the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
The classifier $C_{P,T}(x)$ outputs
\[
{\sf argmax}\ P+\sum_{j=0}^{d-1} T(j)(x_j)
\]
This classifier requires $ndF$ comparisons and additions. Note here  that computing $T(i)(j)(x_j)$ requires a secret look-up in matrix  $T$  based on secret input $x_j$ resulting in $F-1$ comparisons using multiplexers (see
  Section~\ref{sec:impl}). %\nc{Made DG's comment as part of regular text - worth point out}. \cmmt{Is there a +1 etc missing or is this exact?} \nc{By our calculation in Sec 5, it seems that this should be $F/2$ multiplexers}

@@

Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a pointwise dot product, $W_j$'s and $V_j$'s
are matrices of appropriate dimension. The activation function $f$ is given by $f(y) = y$ if
$-1 < y < 1$ and $\mathrm{sign}(y)$ otherwise ($f$ on vectors and matrices are defined point-wise on every element of the vector/matrix). \bonsai can be
seen as a variant of decision trees where the prediction is a function
of the path traversed from root to the leaf and not just the leaf
itself.

@@

\subsubsection*{Linear classifier}The results for linear
classification are in Table~\ref{tab:lc}. The
input and the model are both vectors of length $d$. The columns
``Prev. time'' and ``Prev. comm'' show the time and the total
network communication reported by Bost et al.~\cite{shafindss} for a
network setting with 40ms
round trip time, which is same as our WAN setting. The total execution
time
of \tool generated code in the LAN and the WAN setting is reported
next, followed by the total communication.
We observe that the \tool code performance matches the hand-crafted protocol of Bost
et al., and the programmer effort in \tool is just 20
lines (last column in the table) of high-level code in the \tool
source language. %\aseem{They write circuits,
 % right?} \nc{Actually, they have a specific protocols for dot product and comparison and also say that their developer effort is minimal as they have to write two function calls to these protocols :).} 
 Our execution time is dominated by the multiplications and
boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the
benchmarks as they reflect the number of gates required for a
single 32-bit integer comparison with zero, while the number of
multiplication gates (\#Mul) is the same as the model size $d$.
%% The
%% last column shows the lines of code of \tool program, which is also
%% independent of the model size.

@@

\subsubsection*{Decision trees}
Our decision tree numbers in Table~\ref{tab:dt} further validate
this claim. We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
describe specialized protocols for trees and forests (that perform
better than~\cite{shafindss}).
Similar to Bost et al.~\cite{shafindss}, they also remarks that these
computations are infeasible with Yao-based 2PC.
Again, we observe that
the performance of \tool generated generic 2PC
code is competitive with specialized protocols.

\begin{table*}
\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$  & Prev. time (s) & Prev. Comm (kb) & LAN (s) & WAN (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
\hline
\end{tabular}

 \caption{Linear classification results. We compare our results (columns 5, 6, 7) with~\cite{shafindss} (columns 3 and 4)}
 \label{tab:lc} 
\end{table*}

\begin{table*}
\begin{tabular}{c|c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$ & $F$ & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6 & 13k & 0 & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37 & 750k & 0 & 4219k & 50\\
\hline
\end{tabular}

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
\label{sec:dnneval}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

The first benchmark  is the DNN described in
SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations
(additions and multiplications) 
except for the $\mathsf{argmax}$ at the end of the network.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets}
in \tool.
This DNN also uses square as the activation function and has one
convolution (with 5 output channels) and one fully connected layer. 
Finally, we implement CNN from \minion, that has
two convolutions (with 16 output channels each) and two fully
connected layers.  In contrast to the previous two DNNs, it uses
ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using
arithmetic gates but ReLU requires boolean-and gates.  For a complete
description of these benchmarks and their accuracies, we refer the
reader to the original references.

In Table~\ref{tab:nn}, columns 2 and 3 show the time taken by \minion.
The column ``Model size'' is the number of 32 bit integers in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow it to perform
matrix operations efficiently. In contrast, \tool focuses on generic
2PC, and such optimizations are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
DNN  & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

\subsection{State-of-the-art classifiers}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
\[
 \mathsf{argmax}\ W\matmul x+b
\]
Here, $x$ is a 784 length vector obtained from the input image,
each $W$ is a $10\times 784$ matrix, and each $b$ is a $10$ length
vector. \aseem{Questions on this expression: (1) where is $i$?
  (2) Should $b$ be 10 length vector? (3) Again, should be use $\cdot$
  for matrix multiplication
as we did earlier to be consistent?} \nc{I think I have fixed this. OK now? $\mathsf{argmax}$ throughout this section has implicit use of a dimension and I have left it like that. We can make it explicit if others feel the need.}
We implement this classifer in \tool and present the results in the
first row of Table~\ref{tab:tf}.
Since, we are not aware of any other tools that has used this
model as a benchmark, we only report numbers for \tool.

The next classifer in the Tensorflow tutorial is a convolution neural net with two convolutions
(with 32 output channels) and two fully connected layers with ReLU as the activation function.
This DNN is both bigger and more accurate than the DNNs presented in the previous section.
In particular, it has an accuracy of 99.2\%\footnote{The accuracy of
  the integer model is 0.04\% higher than the floating-point
  model.}. \aseem{Is this footnote necessary? As a reader, I won't
  miss it if it was not there.}\nc{I agree. Happy to remove.}
We observe that this DNN can take a minute per prediction in the WAN
setting and is the largest benchmark that we have evaluated without
partitioning.

@@

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree\footnote{We remark here that our current language does not support functions (which we leave for future work) and with this support, LOC would be even lower.}.\aseem{Should we remark here that once we have functions in the
  language, LOC would come down, perhaps in the footnote? Else a PL
  reviewer might scoff at it :).}\nc{added a footnote.}

@@

\setlength\tabcolsep{4pt}
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm. \\ (Mb)}  & \thead{\#\\And} & \thead{\#\\Mul} & \thead{\#\\Gates} & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

 \caption{Bonsai benchmarks}
 \label{tab:bonsai} 
\end{table}
\setlength\tabcolsep{6pt}
\subsection{Partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines \aseem{Is the limitation machine RAM or ABY
  limit?}\nc{ABY I think. But ABY's limitation is because of RAM I think}. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines. \aseem{Would it be better if we had
  functions, for loop expressions etc.? If so, we should add a
  footnote.}

Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth (the heaviest) stage. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion would run
out of memory but a pipelined \tool implementation would still
succeed. \aseem{Last sentence is speculative? Should we say \minion
  would or could or might?}\nc{I think \minion definitely would, but we could say could to be nice.}

\begin{table}
\begin{tabular}{c|c|c|c |c|c|c}
           &  LAN (s) & WAN (s) & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}

>>>>

To begin, we first implement the benchmarks from Bost et al.~\cite{shafindss}
and \minion~\cite{minionn} (both of which study the same setting),
and show that the performance of the high-level code written in \tool
is comparable to their hand-crafted protocols
(Section~\ref{sec:shallow} and Section~\ref{sec:dnneval}).
%
Next, we demonstrate the generality and programmability aspects of
\tool by implementing state-of-the-art machine learning models from
Tensorflow~\cite{tensorflow} and \bonsai~\cite{bonsai}. Indeed, we
provide the first 2PC implementation of \bonsai.
%
We
implement a Deep Neural Network (DNN) for CIFAR-10
dataset~\cite{cifar} from \minion~\cite{minionn} to illustrate the use
of partitioning in \tool. Finally, we evaluate \tool on the task of matrix factorization~\cite{valeriaMatrix}.

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM.
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Since most of our benchmarks
are related to machine learning, we set up some notation (largely
standard in machine learning) and describe our benchmarks next.

@@

We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. Further, given a vector $x\in\R^d$, we say $\mathsf{argmax}\ x = i$ if $x_i = \mathsf{max}\ \{x_1,\ldots,x_d\}$. We focus on the machine learning models for {\it classification}. A classifier $C$ uses a trained model to {\it predict} a
label $\ell$ for an input data point $x$. For example, given a
data point which is a tuple of humidity and temperature 
a classifier might be able to predict a label as ``will rain'' or ``will not rain''. The {\it
  accuracy} of a classifier refers to the fraction of data points that
the classifier labels correctly from a given set of test data
points.

\subsubsection*{Standard classifiers}
A {\em binary linear classifier} is one of the simplest classifiers. Here,
the input is a data point $x\in\R^d$,
and the model is a vector $w\in\R^d$.
 The possible labels are
$\ell\in\{\mathit{true},\mathit{false}\}$ and the classifier is
$C_w\equiv w^T\matmul x>0$, where $w^T$ denotes the transpose
of matrix $w$, $\matmul$ denotes matrix multiplication (with a vector in this case) and $a>b$ returns $1$ if $a>b$ and $0$ otherwise. 
The {\it model size} of this classifier, i.e., the number of parameters in a model is $d$.
This classifier requires $d$ multiplications, $d-1$
additions, and a single comparison.

A more interesting classifier is {\em Na\"{i}ve Bayes} that predicts labels
from the set $[n]$.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
The model has two matrices: a vector $P$ of length $n$ s.t. for each
$i
\in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood
%that the output label is $i$ for $i\in[n]$.
The other matrix $T$ has size $d\times F\times n$ and for each $j\in
[d], k\in [F], i\in [n]$, the entry $T(j)(k)(i)$ is 
%\equiv\log p(x_j|\ell=i)$, i.e.,
the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
The classifier $C_{P,T}(x)$ outputs
\[
{\sf argmax}\ P+\sum_{j=0}^{d-1} T(j)(x_j)
\]
The additions in the expression above sum $n$-dimensional vectors.
The model size of this classifier is $|P|+|T|$.
This classifier requires $ndF$ comparisons and additions. Note here  that computing $T(i)(j)(x_j)$ requires a secret look-up in matrix  $T$  based on secret input $x_j$ resulting in $F-1$ comparisons using multiplexers (see
  Section~\ref{sec:impl}). %\nc{Made DG's comment as part of regular text - worth point out}. \cmmt{Is there a +1 etc missing or is this exact?} \nc{By our calculation in Sec 5, it seems that this should be $F/2$ multiplexers}

@@

Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a pointwise multiplication of two vectors, $W_j$'s and $V_j$'s
are matrices of appropriate dimensions. The activation function $f$ is given by $f(y) = y$ if
$-1 < y < 1$ and $\mathrm{sign}(y)$ otherwise ($f$ on vectors and matrices are defined point-wise on every element of the vector/matrix). \bonsai can be
seen as a variant of decision trees where the prediction is a function
of the path traversed from root to the leaf and not just the leaf
itself.

@@

\subsubsection*{Linear classifier}The results for linear
classification are in Table~\ref{tab:lc}. The
input and the model are both vectors of length $d$. The columns
``Prev. time'' and ``Prev. comm'' show the time and the total
network communication reported by Bost et al.~\cite{shafindss} for a
network setting with 40ms
round trip time, which is same as our WAN setting. The total execution
time
of \tool generated code in the LAN and the WAN setting is reported
next, followed by the total communication.
We observe that the \tool code performance matches the hand-crafted protocol of Bost
et al., and the programmer effort in \tool is just 20
lines (last column in the table) of high-level code in the \tool
source language. %\aseem{They write circuits,
 % right?} \nc{Actually, they have a specific protocols for dot product and comparison and also say that their developer effort is minimal as they have to write two function calls to these protocols :).} 
 Our execution time is dominated by the multiplications and
boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the
benchmarks as they reflect the number of gates required for a
single  comparison, while the number of
multiplication gates (\#Mul) is the same as the model size $d$.
%% The
%% last column shows the lines of code of \tool program, which is also
%% independent of the model size.

@@

\subsubsection*{Decision trees}
Our decision tree numbers in Table~\ref{tab:dt} further validate
this claim. We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
describe specialized protocols for trees and forests (that perform
better than~\cite{shafindss}).
Similar to Bost et al.~\cite{shafindss}, they also remarks that these
computations are infeasible with Yao-based 2PC.
Again, we observe that
the performance of \tool generated generic 2PC
code is competitive with specialized protocols. 
\setlength\tabcolsep{8pt}
\begin{table*}
\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$  & Prev. time (s) & Prev. Comm (kb) & LAN (s) & WAN (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
\hline
\end{tabular}

 \caption{Linear classification results. We compare our results (columns 5, 6, 7) with~\cite{shafindss} (columns 3 and 4)}
 \label{tab:lc} 
\end{table*}
\setlength\tabcolsep{7pt}
\begin{table*}
\begin{tabular}{c|c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$ & $F$ & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6 & 13k & 0 & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37 & 750k & 0 & 4219k & 50\\
\hline
\end{tabular}

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
\label{sec:dnneval}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and the CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

The first benchmark  is the DNN described in
SecureML~\cite{secureml} (Figure 10 in~\cite{minionn}).
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations
(additions and multiplications) 
except for the $\mathsf{argmax}$ at the end of the network.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} (Figure 11 in~\cite{minionn})
in \tool.
This DNN also uses square as the activation function and has one
convolution (with 5 output channels) and one fully connected layer. 
Finally, we implement CNN from \minion (Figure 12 in~\cite{minionn}), that has
two convolutions (with 16 output channels each) and two fully
connected layers.  In contrast to the previous two DNNs, it uses
ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using
arithmetic gates but ReLU requires boolean-and gates.  For a complete
description of these benchmarks and their accuracies, we refer the
reader to the original references.

In Table~\ref{tab:nn}, columns 2 and 3 show the time taken by \minion.
The column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow it to perform
matrix operations efficiently. In contrast, \tool focuses on generic
2PC, and such optimizations are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length 
\setlength\tabcolsep{6.5pt}
\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
DNN  & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

\subsection{State-of-the-art classifiers}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
\[
 \mathsf{argmax}\ W\matmul x+b
\]
Here, $x$ is a 784 length vector obtained from the input image,
each $W$ is a $10\times 784$ matrix, and each $b$ is a $10$ length
vector.
We implement this classifer in \tool and present the results in the
first row of Table~\ref{tab:tf}. We note that a pure boolean circuit for this functionality cannot fit in the memory of our machines.

The next classifer in the Tensorflow tutorial is a convolution neural net with two convolutions
(with 32 output channels) and two fully connected layers with ReLU as the activation function.
This DNN is both bigger and more accurate than the DNNs presented in the previous section.
In particular, it has an accuracy of 99.2\%.
Since, we are not aware of any other tools that has used this
model as a benchmark, we only report numbers for \tool.
We observe that this DNN can take a minute per prediction in the WAN
setting and is the largest benchmark that we have evaluated without
partitioning.

@@

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree\footnote{We remark here that our current language does not support functions (which we leave for future work) and with this support, LOC would be even lower.}.

@@

\setlength\tabcolsep{3.5pt}
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

 \caption{Bonsai benchmarks}
 \label{tab:bonsai} 
\end{table}
\setlength\tabcolsep{6pt}
\subsection{Partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines.

Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth (the heaviest) stage. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but a pipelined \tool implementation would still
succeed. 
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c}
           &  LAN (s) & WAN (s) & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}
